Time stability in human interaction networks

### 2015-06-19 paper.tex
incorporada contrib do chu no artigo

\subsection{Data and scripts availability}\label{scripts}
As a way to share routines with the scientific community and the whole of the society,
all the software necessary to achieve the results reported in this article,
including all tables and figure of the Supporting Information,
are available through a public domain Python package and an open Git repository~\cite{gmanePack}.

@@

The distribution of vertices in the hubs, intermediary, periphery Erd\"os sectors is remarkably stable along time, provided that a sufficiently large sample of 200 or more messages is considered. 
Moreover, the same distribution applies to the networks of all email lists analyzed, as demonstrated in Figure~\ref{fig:sectIL} of current document and Section~\ref{si:frac} of the Supporting Information. 
Activity is highly concentrated on the hubs, while a very large number of peripheral vertices contribute to only a fraction of the activity. This is expected for a system with a scale-free trace, as confirmed with the data in Table~\ref{autores} for the distribution of activity among participants.

>>>>

\subsection{Availability data and scripts}\label{scripts}
In order to share routines with the scientific community and the whole of the society,
the software necessary to achieve the results reported in this article,
including tables and figures in the Supporting Information,
are available through a public domain Python package and an open Git repository~\cite{gmanePack}.

@@

The distribution of vertices in the hubs, intermediary, periphery Erd\"os sectors is remarkably stable along time, provided that a sufficiently large sample of 200 or more messages is considered. 
Moreover, the same distribution applies to the networks of all email lists analyzed, as demonstrated in Figure~\ref{fig:sectIL} and in Section~\ref{si:frac} of the Supporting Information. 
Activity is highly concentrated on the hubs, while a very large number of peripheral vertices contribute to only a fraction of the activity. This is expected for a system with a scale-free trace, as confirmed with the data in Table~\ref{autores} for the distribution of activity among participants.
